Natural variations in water discharge quantity have an inconsistent impact on sediment transport capacity in subglacial channels

### 2023-10-05 Delaneyetal2023b.tex
more edits

% The rapid increases and decreases in subglacial sediment transport capacity compounds the variability in sediment transport already present in subaerial systems \cite<Figure~\ref{fig:Qw_vari}; >{williams1989,jerolmack2010}.
Sediment transport capacity in subglacial channels responds more rapidly to changes in water discharge compared to their subaerial counter parts \cite{alley1997}.
In subglacial R\"othlisberger channels where water discharge evolves more slowly than channel size or subaerial channels the width-integrated shear stress response to water discharge is $ \tau_{tg}\, \propto\,  Q^{\sim\frac{4}{5}}$ (Table\,\ref{tab:eqs1}).
However, subglacial channels rarely operate in a steady state \cite<e.g.>{gimbert2016}.
For sufficiently short time periods, channel width and wetted area are fixed in the subglacial system (assuming pipe flow) so that the response of width-integrated shear stress is $ \tau_{tg}\, \propto\,  Q^{2}$ (Table\,\ref{tab:eqs1}).
Appendix~\ref{sect:scaling} provides a complete description of sediment transport capacity in different drainage conditions.

>>>>

The rapid increases and decreases in subglacial sediment transport capacity compounds the variability in sediment transport already present in subaerial systems \cite<Figure~\ref{fig:Qw_vari}; >{williams1989,jerolmack2010}.
Sediment transport capacity in subglacial channels responds more rapidly to changes in water discharge compared to their subaerial counter parts \cite{alley1997}.
In subglacial R\"othlisberger channels where water discharge evolves more slowly than channel size or subaerial channels the width-integrated shear stress response to water discharge is $ \tau_{tg}\, \propto\,  Q^{\sim\frac{4}{5}}$ (Table\,\ref{tab:eqs1}).
However, subglacial channels rarely operate in a steady state \cite<e.g.>{gimbert2016}.
For sufficiently short time periods, channel width and wetted area are fixed in the subglacial system (assuming pipe flow) so that the response of width-integrated shear stress is $ \tau_{tg}\, \propto\,  Q^{2}$ (Table\,\ref{tab:eqs1}).
\ref{sect:scaling} provides a complete description of sediment transport capacity in different drainage conditions.
